### 2022-06-27 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_betacov_mapping@6e1ff4016222589bcf665d30237cd734d28d5598 🚀

\hypertarget{host-richness-does-not-predict-virus-distinctiveness}{%
\section{Host richness does not predict virus
distinctiveness}\label{host-richness-does-not-predict-virus-distinctiveness}}

@@

\hypertarget{the-phylogeographic-regions-of-hosts-and-their-viruses-overlap}{%
\section{The phylogeographic regions of hosts and their viruses
overlap}\label{the-phylogeographic-regions-of-hosts-and-their-viruses-overlap}}

@@

\hypertarget{coevolution-informed-emergence-risk-is-different-in-space}{%
\section{Coevolution-informed emergence risk is different in
space}\label{coevolution-informed-emergence-risk-is-different-in-space}}

@@

\hypertarget{human-occupancy-drives-different-levels-of-effective-risk-globally}{%
\section{Human occupancy drives different levels of effective risk
globally}\label{human-occupancy-drives-different-levels-of-effective-risk-globally}}

>>>>

\hypertarget{results-and-discussion}{%
\section{Results and Discussion}\label{results-and-discussion}}

\hypertarget{host-richness-does-not-predict-virus-distinctiveness}{%
\subsection{Host richness does not predict virus
distinctiveness}\label{host-richness-does-not-predict-virus-distinctiveness}}

@@

\hypertarget{the-phylogeographic-regions-of-hosts-and-their-viruses-overlap}{%
\subsection{The phylogeographic regions of hosts and their viruses
overlap}\label{the-phylogeographic-regions-of-hosts-and-their-viruses-overlap}}

@@

\hypertarget{coevolution-informed-emergence-risk-is-different-in-space}{%
\subsection{Coevolution-informed emergence risk is different in
space}\label{coevolution-informed-emergence-risk-is-different-in-space}}

@@

\hypertarget{human-occupancy-drives-different-levels-of-effective-risk-globally}{%
\subsection{Human occupancy drives different levels of effective risk
globally}\label{human-occupancy-drives-different-levels-of-effective-risk-globally}}
